|

### 2022-07-21 paper/paper.Rmd
discussion points
Acknowledgements updated according to German

@@

@@

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr]. The scatterplot matrix of the penguins data was produced by the GGally [@GGally] package built on ggplot2 [@ggplot2] graphics.

>>>>

Other applications

@@

Maybe extensions for slicing

@@

The authors gratefully acknowledge the support of the Australian Research Council and the ResearchFirst undergraduate research program at Monash University. The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr]. The scatterplot matrix of the penguins data was produced by the GGally [@GGally] package built on ggplot2 [@ggplot2] graphics. We thank the Institute of Statistics, BOKU, for their hospitality while part of this work was conducted.
